paper2_resistance_mechanisms_mixtures

### 2016-12-14 inst/documents/paper2/paper2_resistance_mechanisms_mixtures.Rmd
replacing old figures with grid of 4 figures

## ANDY TO DO
1. should I include male exposure prop ?
1. add to intro including about about results in levick et al.
1. work out what's going on with exposure ... why does increasing exposure have a greater effect on mixture than sequential ? 
1. explain resistance-restoration and its relation to selection coefficient
1. expand discussion to include relevance to real world 
1. in discussion address potential criticism that these results are just for a limited region of paramter space (a. point to Levick et al. that explored more of space, b. point to UI that allows readers to explore spce for themselves and identify whether there are places where this does not hold).
1. ? briefly refer to linkage disequilibrium and say we are investigating.

1. can I develop explanatory diagrams to describe the input parameters ?
1. mention other potential effects e.g. differential exposure of M&F, sex linkage, ...
1. add to discussion about relevance of these mechanisms in the field e.g. exposure can be reduced if either insecticide has a repellant effect, which can be set in formulation. (Birget & Koella 2015 mention this not for resistance but for ITNs with repellancy requiring higher coverage for elimination)
1. mention in discussion that repellency would lead to decrease in exposure

@@

@@

```{r, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A. All control inputs equal at 0.5, B. Effectiveness of insecticide1 increased from 0.5 to 0.8, C. Exposure increased to 0.8, D. Effectiveness of insecticide1 and exposure increased to 0.8"}

#4 panel figure

#think about implementing in ggplot2 to make my life easier later ?
#although I'm not sure it would ?

#? allow curves to be thicker

@@

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. All control inputs equal at 0.5, B. Effectiveness of insecticide1 increased from 0.5 to 0.8"}
#effectiveness on mixture

#plot margins
oldpar <- par(mar=c(4, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#base scenario
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.', maxX = 120 )

#plot margins
par(mar=c(4, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#effectiveness1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab="", ylabs = FALSE, main='B.', maxX = 120 )

par(oldpar)

@@

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="Effectiveness of both insecticides 0.8"}

#plot margins
oldpar <- par(mar=c(4, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.8 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), maxX = 120 )

@@

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. Exposure increased to 0.8, B. Exposure and Effectiveness of insecticide1 increased from 0.5 to 0.8"}
#fig.cap seems necessary to keep figs side by side

#plot margins
oldpar <- par(mar=c(4, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.', maxX = 120 )
#cat("Fig. Exposure 0.8 benefit of sequence over mixture increases")

#plot margins
par(mar=c(4, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylabs = FALSE, main='B.', maxX = 120 )
#cat("Fig. Effectiveness 0.8, Exposure 0.8, increased exposure nullifies the effect of increased effectiveness, sequence remains better")
```

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. Dominance of insecticide1 0.8, B. Dominance of both insecticides 0.8"}

#plot margins
oldpar <- par(mar=c(4, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.', maxX = 120 )
#cat("Dominance of insecticide1 0.8")

#plot margins
par(mar=c(4, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.8 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab='', ylabs = FALSE, main='B.', maxX = 120 )
#cat("Dominance of both insecticides 0.8")

par(oldpar)

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. Resistance restoration coefficient allele1 0.8, B. Resistance restoration coefficient both alleles 0.8"}

#plot margins
oldpar <- par(mar=c(4, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.', maxX = 120 )
#cat("Fig. rr_restoration I1 0.8")

#plot margins
par(mar=c(4, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.8 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab='', ylabs = FALSE, main='B.', maxX = 120 )
#cat("Fig. CC. rr_restoration I2 0.2")

par(oldpar)

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. Start frequency allele1 reduced from 0.001, B. as A plus effectiveness insecticide1 increased to 0.8"}

#plot margins
oldpar <- par(mar=c(4, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#P_1 to 0.001 seq remains better
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.', maxX = 150 )

#plot margins
par(mar=c(4, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#P_1 to 0.001 & effect1 to 0.8 mix remains better
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab='', ylabs = FALSE, main='B.', maxX = 150 )

par(oldpar)

@@

## References

>>>>

## ANDY TO DO
1. add to intro including about about results in levick et al.
1. work out what's going on with exposure ... why does increasing exposure have a greater effect on mixture than sequential ? 
1. explain resistance-restoration and its relation to selection coefficient
1. expand discussion to include relevance to real world 
1. in discussion address potential criticism that these results are just for a limited region of paramter space (a. point to Levick et al. that explored more of space, b. point to UI that allows readers to explore spce for themselves and identify whether there are places where this does not hold).
1. ? briefly refer to linkage disequilibrium and say we are investigating.

1. can I develop explanatory diagrams to describe the input parameters ?
1. mention other potential effects e.g. differential exposure of M&F, sex linkage, ...
1. add to discussion about relevance of these mechanisms in the field e.g. exposure can be reduced if either insecticide has a repellant effect, which can be set in formulation. (Birget & Koella 2015 mention this not for resistance but for ITNs with repellancy requiring higher coverage for elimination)
1. mention in discussion that repellency would lead to decrease in exposure
1. is there a refernce to say that the effectiveness of insecticides can be modified at the design stage ?

@@

_TODO rewrite this & probably put effectiveness and exposure in together_
_starting like this_
In the baseline scenario where the effectiveness of both insecticides is set the same at 0.5 the resistance frequencies at each locus for the mixture remain identical (the single solid line in Fig 6A). For this scenario time-to-resistance is longer when the insecticides are used in sequence (dashed lines). Increasing exposure to the insecticides from 0.5 to 0.8 (Fig 6C) decreases the time-to-resistance for both the sequential and mixture strategy and so does not change their relative performance; time-to-resistance remains longer for the sequence.

@@

```{r, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A. All control inputs equal at 0.5 : time-to-resistance is longer for sequential use, B. Effectiveness of insecticide1 increased from 0.5 to 0.8 : time-to-resistance is longer for the mixture, C. Exposure increased to 0.8 : time-to-resistance is longer for sequential use, D. Effectiveness of insecticide1 and exposure increased to 0.8 : time-to-resistance equal for mixture and sequence"}

#4 panel figure looking at effectiveness and exposure

@@

```{r, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A. All control inputs equal at 0.5, B. Resistance restoration for insecticide1 increased from 0.5 to 0.8, C. Dominance for insecticide1 increased to 0.8, D. Resistance restoration and dominance for insecticide1 increased to 0.8"}

#4 panel figure looking at dominance and resistance restoration

#rr1  0.5  0.8
#dom1
#0.5    1   2
#0.8    3   4

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1: 0.5', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

#rr1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1: 0.8', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

#dominance1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

#dom1 & rr1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1: 0.5', line= -2, side=1, cex=0.8) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1: 0.8', line= -2, side=1, cex=0.8) #side=1b,2l,3t,4r

@@

```{r, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A. All control inputs equal at 0.5, starting frequencies of resistance at 0.01, B. Effectiveness for insecticide1 increased from 0.5 to 0.8, C. Starting frequency of resistance for insecticide1 decreased from 0.01 to 0.001, D. Effectiveness for insecticide1 increased from 0.5 to 0.8 and starting frequency for insecticide1 decreased from 0.001 to 0.0001"}

#4 panel figure looking at effectiveness and starting freq.

#eff1  0.5  0.8
#strt freq1
#0.01    1   2
#0.001    3   4

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1: 1%', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 150 )

#eff1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 150 )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1: 0.1%', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

#freq1 0.001
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.6, addLegend=FALSE, main='', maxX = 150 )

#freq1 0.001, eff1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 150 )

@@

```{r, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A. All control inputs equal at 0.5, male exposure 0.8, B. Effectiveness for insecticide1 increased from 0.5 to 0.8, C. Male exposure decreased from 0.8 to 0.2, D. Effectiveness for insecticide1 increased from 0.5 to 0.8 and Male exposure decreased from 0.8 to 0.2"}

#4 panel figure looking at male exposure prop and starting freq.

#eff1  0.5  0.8
#maleprop
#0.8    1   2
#0.2    3   4

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('male exposure: 0.8', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

runcurtis_f2( male_exposure_prop=0.8, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 200 )

#eff1 0.8
runcurtis_f2( male_exposure_prop=0.8, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 200 )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('male exposure:0.2', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

#freq1 0.001
runcurtis_f2( male_exposure_prop=0.2, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.6, addLegend=FALSE, main='', maxX = 200 )

#freq1 0.001, eff1 0.8
runcurtis_f2( male_exposure_prop=0.2, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 200 )

@@

## References
<!-- now auto created here-->
